On exponential sums arising from the classical doubling method

### 2025-03-21 paper.tex
Writing an example

We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ is a character. By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{\algebraicGroup{T},\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
\[
    \exp(\innerproduct{x_{\algebraicGroup{T},\theta}}{y}) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
\]
for large enough $n$. This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.  Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL} (with $\algebraicGroup{T}$ replaced with $\algebraicGroup{T}^{\ast}$), we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.

@@

>>>>

We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\ladicnumbers}$ is a character. By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{\algebraicGroup{T},\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
\[
    \exp(\innerproduct{x_{\algebraicGroup{T},\theta}}{y}) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
\]
for large enough $n$. This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.  Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL} (with $\algebraicGroup{T}$ replaced with $\algebraicGroup{T}^{\ast}$), we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.

@@

\begin{example}
	Take $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$. Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate. Indeed, if $m \ge 2$ is even, then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} = \multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}}$ and $\algebraicGroup{T}_2^{\Frobenius^m} = \multiplicativegroup{\finiteFieldExtension{m}}$. The norm map $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}} \ni \left(x,y\right) \mapsto \FieldNorm{m}{2}\left(x\right) \FieldNorm{m}{2}\left(y\right)$, while the norm map $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \ni x \mapsto \FieldNorm{m}{2}\left(x\right)^{1-q}$. We thus have
	$$\left(\theta \times \theta\right) \circ \aFieldNorm_{ \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius^m} : \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius} } = \theta' \circ \aFieldNorm_{\left(\algebraicGroup{T}'_2\right)^{\Frobenius^m} \colon \left(\algebraicGroup{T}'_2\right)^{\Frobenius}}.$$
\end{example}
